---
title: "p8105_hw6_xl2851"
author: "xinran"
date: "11/15/2019"
output: github_document
---
```{r}
library(tidyverse)
library(modelr)
```
# question 1

```{r}
bw_data= read_csv('./data/birthweight.csv')
```

clean the data

```{r}
bw_tidy=
bw_data%>%
  mutate(
  babysex=as.factor(babysex),
  babysex=recode(babysex,"1"="male", "2"="female"),
  frace=as.factor(frace),
  frace=recode(frace,"1"="white", "2"="black","3"="asian", "4"="puerto rican", "8"="other","9"="unknown"),
  malform=as.factor(malform),
  malform=recode(malform,"1"="present", "0"="absent"),
  mrace=as.factor(mrace),
  mrace=recode(mrace, "1"="white", "2"="black","3"="asian", "4"="puerto rican", "8"="other"))
```

```{r}
anyNA(bw_tidy)
```
The result is FALSE. There is no missing value.
```{r}
# fit a regression using all predictors and do elimataion with alpha = 0.05
all_x = lm(bwt ~ ., data = bw_tidy)
summary(all_x)
# take out 3 predictors because of singularities
step1 = update(all_x, . ~ . -pnumlbw -pnumsga -wtgain)
summary(step1)
# take out frace since frace factor 8 has the highest p-value(0.953745)
step2 = update(step1, . ~ . -frace)
summary(step2)
# take out malform since malformpresent has the highest p-value(0.888937)
step3 = update(step2, . ~ . -malform)
summary(step3)
# take out ppbmi since it has the highest p-value(0.759922)
step4 = update(step3, . ~ . -ppbmi)
summary(step4)
# take out momage since it has the highest p-value(0.530319)
step5 = update(step4, . ~ . -momage)
summary(step5)
# take out menarche since it has the highest p-value(0.245327)
step6 = update(step5, . ~ . -menarche)
summary(step6)
# take out fincome
step7 = update(step6, . ~ . -fincome)
summary(step7)
# take out mrace since one of the races(asian) has p-value>0.05
step8 = update(step7, . ~ . -mrace)
summary(step8)
## Since adjusted R-square got much lower, we need to include mrace
```

```{r}
my_model = lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mheight + parity + ppwt + smoken + mrace, data = bw_tidy)

my_model %>% 
  broom::tidy() %>% 
  knitr::kable()

my_model %>% 
  broom::glance()
```

how to visualize with 2 predictors in a plot?
it should be linear regression?
how to pick predictors? randomly?
plot of model residuals against fitted values(means predicted values?):
what can this plot tell me?
```{r}
bw_tidy %>% 
modelr::add_residuals(my_model) %>% 
modelr::add_predictions(my_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point()+
  geom_hline(yintercept = 0, color = "red") +
  labs(
    title = 'Model residuals against fitted values',
    x = 'Fitted values',
    y = 'Residuals'
  )
```


model 1:

```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = bw_tidy)
model_1 %>% 
  broom::tidy()
```

model 2:

```{r}
model_2= lm(bwt ~ babysex+bhead+blength+babysex*bhead*blength, data = bw_tidy)
model_2 %>% 
  broom::tidy()
```

cross validation
```{r}
cv_df = 
  crossv_mc(bw_tidy, 100)%>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```

```{r}
cv_df = 
  cv_df %>% 
  mutate(my_model = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mheight + parity + ppwt + smoken + mrace, data = .x)),
         model_1= map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         model_2= map(train, ~lm(bwt ~ babysex+bhead+blength+babysex*bhead*blength, data=.x))) %>% 
  mutate(rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)),
         rmse_model1= map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)))
```
warning?prediction from a rank-deficient fit may be misleading

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

# quesion 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

fit a simple linear regression

```{r}
weather_df %>% 
  lm(tmax ~ tmin, data = .) %>% 
  broom::tidy()
```


write a function to draw a bootstrap sample based on a dataframe.

```{r}
boot_sample = function(df) {
  sample_frac(df, size = 1, replace = TRUE)
}
```

```{r}
boot_sample(df = weather_df) %>% 
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(alpha = .5)
```

using modelr

```{r}
bootstrap_weather=
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy),
    glance = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results,glance)
```

r_square

```{r}
weather_r2 = 
  bootstrap_weather %>% 
  select(.id, r.squared)

quantile(weather_r2$r.squared, 0.025)
quantile(weather_r2$r.squared, 0.975)
```
The 95% confidence interval for R-squared is (0.89, 0.93);

```{r}
weather_logbetas = 
  bootstrap_weather %>% 
  group_by(.id) %>% 
  summarize(
    boot_logbetas = log(estimate[[1]]*estimate[[2]])
  )
```

Plot the distribution of your estimates, and describe these in words.

```{r}
weather_r2=
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance))%>% 
  select(-strap, -models) %>% 
  unnest(results)
```

```{r}
weather_r2%>%
  select(r.squared)%>%
  mutate(sd_r2=sd(r.squared),
         mean_r2=mean(r.squared),
         r_low=mean_r2 - qnorm(1-0.05/2)*sd_r2,
         r_high=mean_r2 + qnorm(1-0.05/2)*sd_r2,
         q_2.5=quantile(r.squared,c(.025)),
         q_97.5=quantile(r.squared,c(.975)))%>%
  select(-r.squared)%>%
  head(1)
  
```

```{r}
weather_df %>% 
  lm(tmax ~ tmin, data = .) %>% 
  broom::tidy()
```


